### 2021-04-18 manuscript.rmd
Revert "Adding WC; edit bib; ready for DJ"
This reverts commit a0871bc6430c2b9168db867bec7e769931d3d811.
Anonymized
Fix horrible grammar of footnote 5

[^5]: HDI is one representation of Bayesian credible interval. It is important to note that, like confidence interval, there should be no "correct" choice of the level of credibility, but some established conventions. We choose, like many published works [e.g. @stegmueller:2013:HMC; @kovic:2017:B; @chan2020high], the default value of 95\% is to maintain "compatibility" with traditional approach of reporting 95\% confidence interval. However, there is a general concern about this credibility level as being unstable for Bayesian analysis [@kruschke2014doing]. Some Bayesians, notably, Andrew Gelman, reports very liberal 50\% credible intervals. @mcelreath2020statistical selects 89\% to show the arbitrariness of the practice. @leeuw:2020:AAT select 90\%.

>>>>

[^5]: HDI is one representation of Bayesian credible interval. It is important to note that, like confidence interval, there should be no "correct" choice of the level of credibility but some established conventions. We choose, like many published works [e.g. @stegmueller:2013:HMC; @kovic:2017:B; @chan2020high], the default value of 95\% to maintain "compatibility" with the established convention of reporting 95\% confidence interval. However, there is a general concern about this credibility level as being unstable for Bayesian analysis [@kruschke2014doing]. Some Bayesians, notably, Andrew Gelman, report very liberal 50\% credible intervals. @mcelreath2020statistical selects 89\% to show the arbitrariness of the practice. @leeuw:2020:AAT select 90\%.
